\documentclass[paper=a4,fontsize=10pt,ragged2e,withhyper]{altacv}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%

\geometry{left=1.25cm,right=2cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}
\ifxetexorluatex
% If using xelatex or lualatex:
 \setmainfont{Roboto Slab}
 \setsansfont{Lato}
 \renewcommand{\familydefault}{\sfdefault}
\else
% If using pdflatex:
 \usepackage[rm]{roboto}
 \usepackage[defaultsans]{lato}
% \usepackage{sourcesanspro}
 \renewcommand{\familydefault}{\sfdefault}
\fi
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}%
%
\begin{document}%
\normalsize%

\sloppy%
'
\name{Maria Fernanda Crespo Martinez }
\tagline{Industrial Engineer | Full Stack Software Developer}

\personalinfo{
 \location{Colombia}
}

\makecvheader%

\columnratio{0.6}%
\begin{paracol}{2}%
\cvsection{Experience}
\cvevent{ Project optimization assistant}{UNIVERSIDAD DE SAN BUENAVENTURA CALI}{2016 -- 2017}{}
\begin{itemize}
 \item Maintenance of solar system for home lights the energization.\newline%
Reprogramming and schematization of an intruder security system based on the ATMEGA2560. 
\end{itemize}
\divider
\cvevent{ Electromagnetism physics monitor}{Universidad de San Buenaventura Cali}{2014 -- 2014}{}
\begin{itemize}
 \item Class preparation and group management to resolve doubts regarding electromagnetic and mechanics phenomena. 
\end{itemize}
\divider
\cvevent{Development Engineer}{Real Group Interactive}{2018 -- 2020}{}
\begin{itemize}
 \item Solving challenges to integrate LiDAR technology to georeference 3D scenaries.\newline%
Select and apply new technologies to increase performance analyzing LiDAR data. 
\end{itemize}
\divider
\cvevent{}{Universidad de San Buenaventura Cali}{2014 -- 2014}{}
\divider
\cvevent{}{UNIVERSIDAD DE SAN BUENAVENTURA CALI}{2016 -- 2017}{}
\divider
\cvevent{}{Real Group Interactive}{2018 -- 2020}{}
\divider
\cvevent{}{Women in Data Science (WiDS) at Stanford University}{2019 -- 2019}{}
\begin{itemize}
 \item Volunteer for the WIDS 2019 event realized in Cali {-} Colombia.\newline%
Staff helper and attended to Flask workshop. 
\end{itemize}
\divider
\cvevent{}{TECHO | TETO}{2018 -- 2019}{}
\begin{itemize}
 \item Participated in multiple activities to improve the quality of life of the vulnerable population 
\end{itemize}
\divider
\cvevent{}{Creemos Academy}{2018 -- 2019}{}
\begin{itemize}
 \item Volunteer creating and sharing programming workshops of HTML, CSS and JavaScript for vulnerable kids 
\end{itemize}
\divider
\cvevent{Logistics - Project "Competencias Ciudadanas"}{Universidad del Valle (CO)}{2014 -- 2014}{}
\begin{itemize}
 \item Support in the planning, execution, coordination and logistics of the dialogue events of a formative and cultural nature developed in the project, as well as the events held in the project's visibility phase. 
\end{itemize}
\divider
\cvevent{Software Engineering Student}{Holberton School}{2020 -- 2020}{}
\begin{itemize}
 \item Writer of topics on Software Development:\newline%
• Posted in Analytics Vidhya in Medium: C libraries, a brief summary! — Part 1 (Static libraries).\newline%
• C libraries, a brief summary! — Part 2 (Dinamyc libraries). \newline%
• Posted in The StartUp in Medium: The Magic Behind the Command ls {-}l.\newline%
• Am I a Robot or an object In Python? understanding objects in python. 
\end{itemize}
\divider
\cvevent{Software Engineering Student}{Holberton School}{2020 -- 2020}{}
\begin{itemize}
 \item In this program, I have carried out projects based on low{-}level languages (C), high{-}level languages (Python), web development (Html, CSS, SQL Databases), and DevOps (Linux, Bash).\newline%
•These are the featured projects:\newline%
• Static AirBnB website: Replica of the Airbnb website with pure HTML and CSS.\newline%
• AirBnB Console: Implementation of a storage system for Python objects stored in JSON files, performing the basic operations of a database (Create, Read, Update, Delete).\newline%
• SQL databases: Introduction to structured query language and some complex queries.\newline%
• Simple Shell: In this project, we will create a simple UNIX command interpreter in programming language C.\newline%
• C implementations have been carried out on the most common data structures: hash tables, linked list, double linked list, sorting algorithms, binary trees, among other projects. 
\end{itemize}
\divider
\cvevent{Implementation Leader / Electronic Billing Support. }{QUALITYCOLOMBIA BUSINESS SOLUTION S.A.}{2019 -- 2019}{}
\begin{itemize}
 \item •In this company I had the opportunity to learn and strengthen my soft skills in management, customer service and leadership.\newline%
• Manage the development of new functionalities and bug fixes at the level of electronic billing software.\newline%
• Documentation of bugs and generation of test scenarios for developments.\newline%
• Assignment of projects to implementation consultants.\newline%
• Support creating internal protocols and facing the end customer, in order to optimize processes electronic billing 
\end{itemize}
\divider
\cvevent{Insurance Agent}{SURA insurance company}{2017 -- 2017}{}
\begin{itemize}
 \item •In this job I had the opportunity to get to know my clients better and the way to approach them thinking about their needs and according to their profile.\newline%
Responsibilities:\newline%
• Approach, generation of prospects and relationships with potential clients.\newline%
• Sale of life, business, auto insurance and other solutions offered by the company. 
\end{itemize}
\divider
\cvevent{Software Support Consultant}{QUALITYCOLOMBIA BUSINESS SOLUTION S.A.}{2018 -- 2019}{}
\begin{itemize}
 \item • Training and orientation on the use of the services offered by the company to end customers.\newline%
• Third level support electronic billing projects.\newline%
• Installation of an application server for JAVA Web project on Linux and Windows servers.\newline%
• Software update at the application level and SQL database.\newline%
• Implementation of the electronic billing software. 
\end{itemize}
\divider
\cvevent{}{SURA insurance company}{2017 -- 2017}{}
\divider
\cvevent{}{QUALITYCOLOMBIA BUSINESS SOLUTION S.A.}{2018 -- 2019}{}
\divider
\cvevent{}{Universidad del Valle (CO)}{2014 -- 2014}{}
\divider
\cvevent{}{Holberton School}{2020 -- 2020}{}
\divider
\cvevent{Logistics and Supply Chain Manager}{Produvarios S.A.}{2004 -- 2011}{}
\begin{itemize}
 \item Responsible for the processes inherent to the supply chain (negotiation with suppliers, purchases, demand planning and national and international distribution), as well as stocks and reverse logistics processes, taking care of the level of service and operating costs.\newline%
Responsible for the negotiation and contracts with logistics providers and operators. I managed to reduce transportation costs by 33\%.\newline%
Responsible for sales estimation and demand planning (forecast) for footwear production and foam.\newline%
I was making Follow{-}up of sales indicators, customer service level, \newline%
delivery fulfillment and inventory rotation.\newline%
I was a member of the company's strategic planning and restructuring committee and leader of the process of changing the information system in the area.\newline%
Responsible for planning the supply of finished products for the retail outlet of the footwear line nationwide to mitigate business risks and assure a continuous supply. 
\end{itemize}
\divider
\cvevent{Logistics Manager}{Rubbermix S.A.}{2003 -- 2004}{}
\begin{itemize}
 \item Planning and managing logistics, warehouse, transportation and customer services\newline%
Directing, optimizing and coordinating full order cycle\newline%
Liaising and negotiating with suppliers, manufacturers, retailers and consumers 
\end{itemize}
\divider
\cvevent{Founder}{MFC Social Media Solutions}{2011 -- None}{}
\begin{itemize}
 \item We help businesses discover how to best use social media to connect with customers, drive traffic, generate awareness, and increase sales.\newline%
Our mission is to help you navigate the constantly changing social media jungle. 
\end{itemize}
\divider
\cvevent{Planning and Procurement Coordinator}{Omnilife Manufactura de Colombia Ltda.}{2001 -- 2003}{}
\begin{itemize}
 \item Created the Procurement and Logistics Department.\newline%
Kept track of quality, quantity, stock levels, delivery times, transport costs and efficiency\newline%
Led the export plan of finished product to South America.\newline%
Established the supplier certification policy. 
\end{itemize}
\divider
\cvevent{Co-Founder}{ExpoMimarte - Aluna Group SAS}{2018 -- None}{}
\begin{itemize}
 \item Expomimarte Fair is Cali’s biggest and best exhibition covering all things pregnancy and baby related.\newline%
We have gathered the baby brands under one roof as well as Cali’s leading retailers and product specialists. In addition, we also have Cali’s top pregnancy \& baby professionals ready to give you the best and latest advice and address any concerns or questions you might have about this exciting yet daunting time of life.\newline%
Lore, Anita y Mafe, are the founders of Aluna Group which is the company that runs the ExpoMimarte Fair. Lore first came up with the idea of the Pregnancy \& Baby Fair when she was pregnant with her first child Simon. She wanted to be able to attend a show where she could view, try, test and buy the safest and best baby products on the market. Along with Anita y Mafe, she made this dream a reality and today, the ExpoMimarte Fair offers this, along with big discounts, expert advice and many free samples and goody bags. 
\end{itemize}
\divider
\cvevent{Live Team Production}{DataFactory}{2017 -- None}{}
\begin{itemize}
 \item Executed CONCACAF's social media marketing and website strategies during the different tournaments of the federation to increase web traffic and brand loyalty.\newline%
Produced personalized pieces of content with the necessary quality to position and increase the traffic in social media and web of the Ambito Financiero brand.\newline%
Posted articles for Gol TV in real{-}time on social networks and web.\newline%
Generated live sports data to turn it into truthful information. 
\end{itemize}
\divider
\cvevent{Full Stack Software Developer}{Holberton School Colombia}{2020 -- None}{}
\begin{itemize}
 \item Holberton School is a project{-}based alternative to college for the next generation of software engineers.\newline%
School Projects\newline%
C Programming Language, Linux:\newline%
• Printf: Clone of the printf function included in the C standard library.\newline%
URL: https://github.com/mfcrespo/printf\newline%
• Monty Interpreter: The creation of an interpreter to use stacks and queues (LIFO and FIFO).\newline%
URL: https://github.com/mfcrespo/monty\newline%
• Simple Shell: Simple version of the shell that comes by default in Linux systems, in other words, it is an interpreter that reads from standard input or from a file and executes the commands read through the bash.\newline%
URL: https://github.com/mfcrespo/simple\_shell\newline%
Python3:\newline%
• AirBnB Clone: Back{-}end console deployment for an Airbnb clone app, front{-}end and RESTful API. The console is a command line interpreter that is used to manage and manipulate the application classes. Further, this project exposes all objects stored via a JSON web interface and manipulate the objects via a RESTful API. I worked in python, flask, HTML, css and mysql.\newline%
URL: https://github.com/mfcrespo/AirBnB\_clone\_v3 
\end{itemize}
\divider
\cvevent{Coordinator of the Procurement Consolidation Program}{CIAT Centro Internacional de Agricultura Tropical}{2000 -- 2001}{}
\begin{itemize}
 \item Implemented the supplier certification policy\newline%
I Decreased stocks of the General Warehouse by 75\%.\newline%
I managed to increase the level of acceptance and application of the processes among users.\newline%
Improved the delivery times of orders to users by 65\% 
\end{itemize}
\divider
\cvevent{}{CIAT Centro Internacional de Agricultura Tropical}{2000 -- 2001}{}
\divider
\cvevent{}{DataFactory}{2017 -- None}{}
\divider
\cvevent{}{Rubbermix S.A.}{2003 -- 2004}{}
\divider
\cvevent{}{Omnilife Manufactura de Colombia Ltda.}{2001 -- 2003}{}
\divider
\cvevent{}{Holberton School Colombia}{2020 -- None}{}
\divider
\cvevent{}{MFC Social Media Solutions}{2011 -- None}{}
\divider
\cvevent{}{Produvarios S.A.}{2004 -- 2011}{}
\divider
\cvevent{}{ExpoMimarte - Aluna Group SAS}{2018 -- None}{}%
\cvsection{Projects}
\cvevent{}{}{None -- None}{}
\begin{itemize}
 \item Simple replication of the command{-}line interpreter Shell. All files are written in C language.
\end{itemize}
\divider
\cvevent{}{}{None -- None}{}
\begin{itemize}
 \item The goal of the project is to deploy on your server a simple copy of the website. This project must be composed at the end of its development by:\newline%
A command interpreter to manipulate data without a visual interface, like in a Shell (perfect for development and debugging)\newline%
A website (the front{-}end) that shows the final product to everybody: static and dynamic\newline%
A database or files that store data (data = objects)\newline%
An API that provides a communication interface between the front{-}end and your data (retrieve, create, delete, update them)
\end{itemize}%

\switchcolumn%

\cvsection{Summary}
I´m Industrial Engineering, an expert in the supply chain, customer service, e-commerce, and social media marketing. I dedicate myself to generate and manage change processes based on making results and profits. I support the content generation processes, brand positioning and planning. I focus myself in improvement company´s processes, according to the needs of the environment.

I strongly believe in teamwork, being strategic, thinking outside the box, and following discipline until you get the result that adds value to the company. I am passionate about leading teams and working in a matrix environment, as part of a global organization where there are many media outlets. I have passion for results and connectivity.

My academic background is B.E. in Industrial Engineering from the Pontificia Universidad Javeriana, Logistics Management from the Universidad del Valle and Software Developer from Holberton School. %

\cvsection{Skills}
\cvtag{Git}
\cvtag{C}
\cvtag{JavaScript}
\cvtag{Microsoft Excel}
\cvtag{Linux}
\cvtag{Microsoft PowerPoint}
\cvtag{Bash}
\cvtag{HTML}
\cvtag{Python}
\cvtag{Microsoft Word}
\cvtag{Bases de datos}
\cvtag{Sistemas de planificación de recursos empresariales}
\cvtag{Strategic Planning}
\cvtag{Supply Chain Management}
\cvtag{Public Relations}
\cvtag{Social Media Marketing}
\cvtag{Marketing Strategy}%

\cvsection{Education}
\cvevent{Technologist in analysis and development of information systems}{Servicio Nacional de Aprendizaje (SENA)}{2017 -- 2020}{}
\divider
\cvevent{Full Stack Engineer}{Holberton School}{2020 -- 2022}{}
\begin{itemize}
 \item Learning the Linux Kernel capabilities by reproducing C standard library functions and command{-}line tools. Fundamentals of network communication, parallel programming, and advanced data structures and algorithms. 
\end{itemize}
\divider
\cvevent{Grado en Ingeniería}{Universidad de San Buenaventura}{2012 -- 2017}{}
\begin{itemize}
 \item Distinction of Academic Excellence {-} 2017 
\end{itemize}
\divider
\cvevent{Pedagogy Program for Non-Licensed Professionals}{Universidad del Valle (CO)}{2015 -- 2015}{}
\begin{itemize}
 \item Provide the non{-}licensed professionals who participate in the study, the necessary tools for adequate knowledge of the teaching work in order to optimize their profession at the service of the educational institutions of which they will be part. 
\end{itemize}
\divider
\cvevent{Technological Specialization Quality Methodologies for Software Development}{National Learning Service known as (SENA)}{2019 -- 2019}{}
\begin{itemize}
 \item In this program, the review and contextualization of different methodologies for software development were carried out, focusing on SCRUM, PSP and TSP. 
\end{itemize}
\divider
\cvevent{Electronic Technologist}{Universidad del Valle (CO)}{2011 -- 2014}{}
\begin{itemize}
 \item Electronic technologist with training in research, design and execution of projects in different areas with multidisciplinary teams in order to seek comprehensive solutions. Foundation in digital electronics, Microcontrollers, PLC, power electronics, among others. 
\end{itemize}
\divider
\cvevent{Software Engineer }{Holberton School}{2020 -- 2020}{}
\begin{itemize}
 \item Holberton School is a software school headquartered in San Francisco with campuses in Colombia, France, Mexico, Uruguay, and Tunisia. Its goal is to empower the software developers of the future with a curriculum created to give students hands{-}on programming experience and help them develop soft skills to make a difference in the world of technology and software development. The Holberton School methodology uses project{-}based learning and peers learning to provide the tools necessary to adapt to the future and ever{-}changing technologies. 
\end{itemize}
\divider
\cvevent{Information Systems Technologist}{Universidad del Valle (CO)}{2017 -- 2021}{}
\divider
\cvevent{English Course I}{Unidad Central de Valle}{2014 -- 2014}{}
\divider
\cvevent{Logistics Manager}{Universidad del Valle (CO)}{2002 -- 2003}{}
\divider
\cvevent{Full Stack Software Developer}{Holberton School}{2020 -- 2021}{}
\begin{itemize}
 \item Holberton School is a San Francisco{-}based software school. Its goal is to empower the software developers of the future with a curriculum created to give students hands{-}on programming experience and help them develop soft skills to make a difference in the world of technology and software development. The Holberton School methodology uses project{-}based learning and peers learning to provide the tools necessary to adapt to the future and ever{-}changing technologies. 
\end{itemize}
\divider
\cvevent{Industrial Engineering}{Pontificia Universidad Javeriana}{2020 -- 2021}{}%

\end{paracol}%
\end{document}